Weather Data Integration and Assimilation System\\

### 2020-02-09 thesis.tex
Thesis - There has to be a space/tab between abbreviation and its expansion.

\addcontentsline{toc}{chapter}{List of Abbreviations} 
\printglossary[type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
\dbc{There has to be a space/tab between abbreviation and its expansion.}

>>>>

\newglossarystyle{custom-glossary-style}{%
  \setglossarystyle{long}%
  \renewenvironment{theglossary}%
    {\begin{longtable}[l]{@{}p{\dimexpr 4cm-\tabcolsep}p{0.8\hsize}}}% <-- change the value here
    {\end{longtable}}%
}

\addcontentsline{toc}{chapter}{List of Abbreviations} 
\printglossary[style=custom-glossary-style, type=\acronymtype, title=List of Abbreviations, toctitle=List of Abbreviations, nonumberlist]
